Interval Probability for Fuzzy Quantum Theories

### 2016-07-27 prob.tex
prob.tex Fix typos and citations...

\begin{thm}[Shapley~\cite{Shapley1965,GilboaSchmeidler1994}]
Every convex interval-valued probability measure has a nonempty core,
where an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
is convex if $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$
and $l\left(E_{1}\cup E_{2}\right)\le l\left(E_{1}\right)+l\left(E_{2}\right)-l\left(E_{1}\cap E_{2}\right)$
for all $E_{1},E_{2}\in\events$.\qed\end{thm}

@@

\begin{definition}[Ideal Measurement; Complement;
Commutativity~\cite{Swart2013,peres1995quantum,Griffiths2003}]~
\begin{itemize}
\item A set of mutually orthogonal projections $P_{i}$ is called an \emph{ideal
measurement} if it is a partition of the identity, i.e.,
$\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$.
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called \emph{complement}. It is orthogonal to $P$,
and corresponds to the complement event~$\Omega\backslash E$
in classical probability.
\item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical intersection
between events. 
\end{itemize}
\qed\end{definition}

>>>>

\begin{thm}[Shapley~\cite{Shapley1965,GilboaSchmeidler1994}]
Every convex interval-valued probability measure has a nonempty core,
where an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
is convex if $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$
and $l\left(E_{1}\cup E_{2}\right)+l\left(E_{1}\cap E_{2}\right)\ge l\left(E_{1}\right)+l\left(E_{2}\right)$
for all $E_{1},E_{2}\in\events$.\qed\end{thm}

@@

\begin{definition}[Ideal Measurement; Complement; Commutativity]~ 
\begin{itemize}
\item A set of mutually orthogonal projections $P_{i}$ is called an \emph{ideal
measurement} if it is a partition of the identity, i.e., $\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$~\cite{Swart2013}. 
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called \emph{complement}. It is orthogonal
to $P$, and corresponds to the complement event~$\Omega\backslash E$
in classical probability~\cite{Griffiths2003}. 
\item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical
intersection between events~\cite{peres1995quantum}. 
\end{itemize}
\qed\end{definition}
